A seamless, client-centric programming model for type safe web applications

### 2014-05-02 paper.tex
F# -> F\#

\paragraph{AFAX} AFAX\ \cite{afax}, an F#-based solution, takes an approach
quite similar to ours, using monads to allow client and server side to coexist
in the same program. Unfortunately, using F# as the base of such a solution
raises the issue of side effects. Since any expression in F# may be side
effecting, it is quite possible with AFAX to perform a side effect on the client
and then attempt to perform some action based on this side effect on the server.
To cope with this, AFAX needs to introduce cumbersome extensions to the F# type
system, making AFAX exclusive to Microsoft's F# compiler and operating system,
whereas our solution is portable to any pair of Haskell compilers.

@@

\bibitem[Petricek, Syme (2007)]{afax}
T. Petricek, and Don Syme. "AFAX: Rich client/server web applications in F#." (2007).

>>>>

\paragraph{AFAX} AFAX\ \cite{afax}, an F\#-based solution, takes an approach
quite similar to ours, using monads to allow client and server side to coexist
in the same program. Unfortunately, using F\# as the base of such a solution
raises the issue of side effects. Since any expression in F\# may be side
effecting, it is quite possible with AFAX to perform a side effect on the client
and then attempt to perform some action based on this side effect on the server.
To cope with this, AFAX needs to introduce cumbersome extensions to the F\#
type system, making AFAX exclusive to Microsoft's F\# compiler and operating
system, whereas our solution is portable to any pair of Haskell compilers.

@@

\bibitem[Petricek, Syme (2007)]{afax}
T. Petricek, and Don Syme. "AFAX: Rich client/server web applications in F\#." (2007).
